Some lessons after the formalization of the ctm approach to forcing \thanks{Supported by Secyt-UNC project 33620180100465CB and Conicet.}

### 2022-05-29 Independence_CH/proof_assists_isabelle.tex
minor changes.

In contrast with LCF, some of the more prominent ITPs of today are
based on some type theory. Both Coq~\cite{coq} and
lean~\cite{DBLP:conf/cade/Moura021} are based on the Calculus of
Inductive Constructions
\cite{DBLP:conf/mfps/PfenningP89,DBLP:journals/iandc/CoquandH88},
while Agda~\cite{agda} is an extension of Martin-Löf type
theory~\cite{DBLP:books/daglib/0000395}. The oldest ITP still
still used today is Mizar~\cite{mizar} is far away both in terms
of foundations and architecture; it inspired, though, the Isar
dialect used in nowadays Isabelle.

>>>>

In contrast with LCF, some of the more prominent ITPs of today are
based on some type theory. Both Coq~\cite{coq} and
lean~\cite{DBLP:conf/cade/Moura021} are based on the Calculus of
Inductive Constructions
\cite{DBLP:conf/mfps/PfenningP89,DBLP:journals/iandc/CoquandH88},
while Agda~\cite{agda} is an extension of Martin-Löf type
theory~\cite{DBLP:books/daglib/0000395}. Mizar~\cite{mizar} is the
oldest ITP still used today but is far away both in terms of
foundations and architecture from Isabelle; Mizar inspired, though, the
Isar dialect used in nowadays Isabelle.
